Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-01 02_Paper/paper.tex
Chapter 3

@@

Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique. This method is executed by
an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation. In a further step, the findings would be later corrected by other person than the auditor \cite{fox1993quality}.

@@

Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.

While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Generally, statistical methods are faster than hundred percent controls, however, their disadvantage is that those methods are based on assumptions. those assumptions might lead to errors if the variance of the product quality higher than expected.

@@

Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature. This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area. Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}. Considering the lack of literature, our goal is to decrease this gap on the research area by implementing a functional predictive model in quality assurance for an assembly process and describing the lesson learned during this implementation.

@@

In our work we applied a case-based research approach \cite{yin2017case} to answer the research question. 
One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.
In addition case-based research approaches have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....). % @Lennart: hier müssen entsprechend Beispiele eingetragen werden
\AP{ 
       - How does the previous sentences apply to the democell?
       - This suits better in the methods section}
       - Review

@@

\begin{itemize}
       \item Assemble errors due to robotic arm
       \item Bearing damage on the conveyor belt
       \item Resistance on the conveyor belt
       \item Leakage in the compressed air system
       \item Productivity limit reached
       \item Missing material
\end{itemize}

@@

The continuous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations. With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner. The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability. This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.

@@

The first step to collect the data is to list all the variables of interest and to map their source. The second step is to determine the use cases of interest.  On this research, we focussed on the data described on Table.~\ref{tab:data_source} and the six use cases described on Table.~\ref{tab:use_cases}. The data was manually collected by using the software "UAExperts". Aproximately 15 hours of data was collected, by equally sampling each use case during the data acquisition time.

\begin{table}
       \centering
       \begin{adjustbox}{width=.45\textwidth}
       \begin{tabular}{ c c c } \toprule
              \textbf{Data of interest} & \textbf{Server Source} & \textbf{Variable}\\ \midrule
              Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item Conveyor: Gate
                     \item Conveyor: QC
                     \item Conveyor: Store
                     \end{description}
                     \end{minipage} \\ \hline
              UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item $xyz$ Gripper position
                     \end{description}
                     \end{minipage} \\ \hline
              Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item UR3 gripper open/close
                     \item Grab/drop disk based on disk type
                     \end{description}
                     \end{minipage} \\ \hline
              Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item OK-NOK label
                     \item $xy$ disk deviation from center point
                     \item Absolute disk deviation
                     \end{description}
                     \end{minipage} \\ \hline
              Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item Position
                     \item Speed
                     \item Safe to go
                     \end{description}
                     \end{minipage} \\ \hline
              Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     \begin{description}
                     \item Disk Size
                     \end{description}
                   \end{minipage} \\ \bottomrule
       \end{tabular}
       \end{adjustbox}
       \caption{Industriy 4.0 demonstration cell: Relevant data with its reference source server}
       \label{tab:data_source}
\end{table}

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Decision Tree         & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
                Random Forest classification on our annomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}

>>>>

This paper is divided in 6 sections:

\begin{itemize}
       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
\end{itemize}

@@

Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique. This method is executed by
an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation. In a further step, the findings would be later corrected by another person rather than the auditor \cite{fox1993quality}.

@@

Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and the hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.

While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions. those assumptions might lead to errors if the variance of the product quality higher than expected.

@@

Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature. This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area. Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}. Considering the lack of literature, our goal is to decrease this gap on the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation.

@@

To test our theories, we need to select the right testing platform. This platform should represent real industrial applications and be able to handle a certain level of complexity. In our work, we applied a case-based research approach \cite{yin2017case} in order to answer the research question. One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.

@@

\begin{itemize}
       \item Assemble errors due to the robotic arm
       \item Bearing damage on the conveyor belt
       \item Resistance on the conveyor belt
       \item Leakage in the compressed air system
       \item Productivity limit reached
       \item Missing material
\end{itemize}

@@

The continuous data collection and the clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations. With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner. The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability. This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.

@@

The first step to collect the data is to list all the variables of interest and to map their source. The second step is to determine the use cases of interest.  On this research, we focussed on the data described on Table.~\ref{tab:data_source} and the six use cases described on Table.~\ref{tab:use_cases}. The data was manually collected by using the software "UAExperts". Approximately 15 hours of data was collected, by equally sampling each use case during the data acquisition time.

\begin{table}
       \centering
       \begin{adjustbox}{width=.45\textwidth}
       \begin{tabular}{ c c c } \toprule
              \textbf{Data of interest} & \textbf{Server Source} & \textbf{Variable}\\ \midrule
              Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item Conveyor: Gate
                     \item Conveyor: QC
                     \item Conveyor: Store
                     \end{description}
                     \end{minipage} \\ \hline
              UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item $xyz$ Gripper position
                     \end{description}
                     \end{minipage} \\ \hline
              Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item UR3 gripper open/close
                     \item Grab/drop disk based on disk type
                     \end{description}
                     \end{minipage} \\ \hline
              Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item OK-NOK label
                     \item $xy$ disk deviation from the center point
                     \item Absolute disk deviation
                     \end{description}
                     \end{minipage} \\ \hline
              Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item Position
                     \item Speed
                     \item Safe to go
                     \end{description}
                     \end{minipage} \\ \hline
              Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     \begin{description}
                     \item Disk Size
                     \end{description}
                   \end{minipage} \\ \bottomrule
       \end{tabular}
       \end{adjustbox}
       \caption{Industriy 4.0 demonstration cell: Relevant data with its reference source server}
       \label{tab:data_source}
\end{table}

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Decision Tree         & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
                Random Forest classification on our anomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}
